Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-10 paper/paper.tex
minor changes on intro

Figure~\ref{fig:workflow} illustrates the infrastructure we used in
this study.
The bug-finding process
takes on input JS files from regression test suites of various JS
engines and generates warnings on output. Boxes in the figure denote encapsulation;
arrowed lines indicate control flow (dashed) and data flow
(filled). The cycle icons denote repetition--the leftmost icon
indicates that each file in the input list will be analyzed in
separate whereas the rightmost icon shows that a single file will be
fuzzed multiple times. The bug-finding process works as follows.  Considering the case
where fuzzing is not selected, as illustrated in the inner box at the bottom
of the figure, the oracle checks whether or not the output produced
for that file is consistent across all engine implementations. In case
the test passes in all engines or fails in all engines (\ie{}, the
output is consistent), the infrastructure discards the corresponding
input. Otherwise, it considers the input as potentially
fault-revealing; hence interesting for human inspection. Considering
the case where fuzzing~\cite{fuzz-testing-history} is selected, new
inputs are obtained from a given input using some off-the-shelf
fuzzer. Several fuzzing methods have been proposed in the
  past, varying with respect to how new inputs are generated (\eg{},
  coverage-based~\cite{afl,honggfuzz},
  grammar-based~\cite{grammarinator,jsfunfuzz}, and
  random-based~\cite{radamsa}). Section~\ref{sec:objects:fuzzers} describes the
  fuzzers we selected. The workflow of the infrastructure with fuzzing
  enabled is similar to that of no fuzzing. In this case, however, multiple warnings can be produced
for a given seed input.

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases when the anomaly has been
detected during the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}, \Igor{crashes (ie. FatalError) and core dumps 
  are considered HI group as well}. The rationale is that
the test in this group executed without violating any internal checks
of the API. In constrast, warnings in the LO group reflect the cases where the
anomaly was observed during the execution of some standard JS
function.
\Mar{is this correct? what are those?}\Igor{Yeah, it's okay}We
found that different engines often check the pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a pre-condition that another engine does not, 
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
\Igor{these cases happen because the specification describes how a function
should work, however the internal implementation is defined by the engine developers}.
In those cases,
our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only 12\% of the reals bugs
we found originated from the LO category. \Mar{show real examples of
  HI and LO.}
\Igor{For example, a bug caught by our environment and reported as LO priority was reported 
on Chakra engine, the JS code can be found in Figure~\ref{fig:lo-priority}. In this case,
this is a seed from Mozilla suite (\CodeIn{mozilla/non262/statements/for-in-with-assignments.js}),
the warning was not caught by the \CodeIn{assertEq} function that compares if two arguments are equals, 
the bug appears inside the generator function\footnote{Generators \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Statements/function*}}
at line 2. According to ES6 specification\footnote{ES6 YieldExpression \url{https://www.ecma-international.org/ecma-262/8.0/index.html\#prod-YieldExpression}},
it is allowed the use of \CodeIn{yield in} in a \CodeIn{for} loop. In our infrastructure,
only Chakra engine fails with an error output \CodeIn{SyntaxError: Syntax error}, due
the output does not shows nothing related with assertions, we considered this one as a warning from LO group.
Until now, the issue was confirmed and waiting for merge/closed.
\Fix{checar ate o prazo de submissao. Essa issue esta confirmada e com commits, falta apenas o merge.}
}
\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function},
  }
  \begin{lstlisting}
function* g1() {
  for (var x = yield in {}) ;
}
var it = g1();
assertEq(it.next().done, false);
assertEq(it.next().done, true);
  \end{lstlisting}
  \normalsize
  \caption{Bug caught by our environment as LO priority.}
  \label{fig:lo-priority}
  \end{figure}

An example of a warning from the HI group is defined in Figure~\ref{fig:hi-priority}. 
This is a testcase from WebKit.es6 suite that it was mutate by radamsa fuzzer, the 
initial seed has in line 3 the code \CodeIn{"foo".repeat(3)} but the fuzzer changed the 
integer 3 to a big integer number. We reported this case in chakra due a core dumps that occurs
during the runtime, however this case was rejected due \CodeIn{incompatibility by design} that
this is an intentional behavior of engine that crash the process if it runs out of memory
\footnote{Chakra issue \#4979 \url{https://github.com/Microsoft/ChakraCore/issues/4979}}.

@@

\subsection{Seed JS files\label{sec:seeds}}~We considered test suites
associated with all four JS engines we analyzed
(section~\ref{sec:methodology:engines}). In addition, we mined tests
from other GitHub repositories based on the following selection
criteria--the project must have received at least 1K stars and the
project must not use external libraries. Figure~\ref{fig:query}
illustrates the GitHub API query~\cite{github-rest-api} we used to
find javascript engines projects defined by the label
``javascript-engine''.  The resulting list included a total of 33 projects.
\Igor{
  Due the GitHub does not supports to get the repository files via API, we
  analyzed manually each of them. It was observed that sixteen projects
  are invalid for us due the uses NodeJS that our engine cannot support it,
  empty repositories and browser support as well and another 13 projects 
  does not have a test module in their repository.
  A total of 4 projects remained after the manual inspection, two of them
  are added before, for example the V8\footnote{The official mirror of the V8 Git repository \url{https://github.com/v8/v8}}
  and V7\footnote{V7 Embedded JavaScript engine \url{https://github.com/cesanta/v7}} repositories.
  The Duktape and JerryScript tests are the seeds that we integrate on our infraestruture.
  The repositories of JSI and TinyJS are found manually and was incorpored also even less 1K of stars.
}

\begin{figure}[h]
  \centering
  \begin{lstlisting}
https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000
  \end{lstlisting}
  \caption{\label{fig:query}
  Query used to find JS engine projects with over 1K stars.
  }
\end{figure}

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites\Mar{try to use a single
      name (if possible) to facilitate reference in the paper. Use the
  full path in the URL (citation) to indicate where one can find those
  files.}}
  \begin{tabular}{ccr}
    \toprule
    TestSuite & Source & \# JS files \\
    \midrule
    Duktape & \cite{duktape} & 997 \\
    JerryScript & \cite{jerryscript} & 1,803 \\
    JSI & \cite{jsi} & 99 \\
    Tiny-js & \cite{tinyjs} & 44 \\
    Mozilla & \Fix{??} & 32,414 \\
    V8.test.benchmarks.data & \Fix{??} & 64 \\
    WebKit.jstests.es6 & \Fix{??} & 605 \\
    WebKit.jstests.microbenchmarks & \Fix{??} & 426 \\
    \midrule
     &  & 36,452 \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued by our team since April,
    2018. The analysis of warnings was not uninterrupted.}
  \label{tab:bugs}
  \begin{tabular}{cccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Priority & Seed \\
    \midrule    
    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & HI & webkit.jstests.es6 \\ 
    2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979} & HI & webkit.jstests.es6 \\
    3  & 4/14 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}  & HI & webkit.jstests.es6    \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749} & HI & JerryScriptjs.ecma      \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033} & HI & mozilla      \\
    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038} & HI & JerryScriptjs.ecma   \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065} & HI & mozilla
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} & \multirow{2}{*}{HI} & \multirow{2}{*}{mozilla}\\
                        &  &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}  &   & \\
    \midrule    
    9  & 4/29 & radamsa & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}  & HI  & JerryScriptjs.ecma\\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} & \multirow{2}{*}{HI} & \multirow{2}{*}{tinyjs.tests}\\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156} &  & 
    \\
    \midrule    
    11 & 5/02 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197} & LO & mozilla \\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208} & HI & mozilla \\
    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} & HI & JerryScriptjs.regression \\
    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} & HI & v8.test.benchmarks\\
    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} & HI & webkit.jstests.es6\\
    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} & LO & mozilla\\
    17 & 5/24 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943} & HI & webkit.jstests.es6\\
    18 & 6/26 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScriptjs.regression\\
    19 & 6/28 & \crossmark & Chakra & Confirmed  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & webkit.jstests.es6\\
   \bottomrule     
  \end{tabular}
\end{table*}

@@

>>>>

Figure~\ref{fig:workflow} illustrates the infrastructure we used in
this study.
The bug-finding process
takes on input JS files from regression test suites of various JS
engines and generates warnings on output. Boxes in the figure denote encapsulation;
arrowed lines indicate control flow (dashed) and data flow
(filled). The cycle icons denote repetition--the leftmost icon
indicates that each file in the input list will be analyzed in
separate whereas the rightmost icon shows that a single file will be
fuzzed multiple times. The bug-finding process works as follows.  Considering the case
where fuzzing is not selected, as illustrated in the inner box at the bottom
of the figure, the oracle checks whether or not the output produced
for that file is consistent across all engine implementations. In case
the test passes in all engines or fails in all engines (\ie{}, the
output is consistent), the infrastructure discards the test. Otherwise, it considers the input as potentially
fault-revealing; hence interesting for human inspection. Considering
the case where fuzzing~\cite{fuzz-testing-history} is selected, new
inputs are obtained from a given input using some off-the-shelf
fuzzer. Several fuzzing methods have been proposed in the
  past, varying with respect to how new inputs are generated (\eg{},
  coverage-based~\cite{afl,honggfuzz},
  grammar-based~\cite{grammarinator,jsfunfuzz}, and
  random-based~\cite{radamsa}). Section~\ref{sec:objects:fuzzers} describes the
  fuzzers we selected. The workflow of the infrastructure with fuzzing
  enabled is similar to that of no fuzzing. In this case, however, multiple warnings can be produced
for a given seed input.

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases when the anomaly has been
detected during the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}, crashes (ie. FatalError) and core dumps 
  are considered HI group as well. The rationale is that
the test in this group executed without violating any internal checks
of the API. In constrast, warnings in the LO group reflect the cases where the
anomaly was observed during the execution of some standard JS
function.
\Mar{is this correct? what are those?}We
found that different engines often check the pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a pre-condition that another engine does not, 
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
\Igor{these cases happen because the specification describes how a function
should work, however the internal implementation is defined by the engine developers}.
In those cases,
our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only 12\% of the reals bugs
we found originated from the LO category. \Mar{show real examples of
  HI and LO.}

\subsection{ES6 design}
\Fix{to appear}
% no-bug low console output

% bug high console output

@@

\subsection{Seed JS files\label{sec:seeds}}~We considered test suites
associated with all \Fix{four} JS engines we analyzed
(section~\ref{sec:methodology:engines}).
\Igor{
  We selected only the seeds that supports integration without external dependencies. 
  In addition, we found in public repositories (ie. GitHub) several kinds of projects 
  that contains javascript files, however, the most of them uses nodejs that have 
  internal functions that our engines does not support. 
  We found a total of four engines projects that we can integrate to our seeds 
  with minor fixes on the files, due the "assertion function" is missing in some cases.
}

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites
  % \Mar{try to use a single
  %     name (if possible) to facilitate reference in the paper. Use the
  % full path in the URL (citation) to indicate where one can find those
  % files.}
  }
  \begin{tabular}{ccr}
    \toprule
    TestSuite & Source & \# JS files \\
    \midrule
    Duktape & \cite{duktape} & 997 \\
    JerryScript & \cite{jerryscript} & 1,803 \\
    JSI & \cite{jsi} & 99 \\
    Tiny-js & \cite{tinyjs} & 44 \\
    Mozilla & \cite{mozilla} & 32,414 \\
    V8 & \cite{v8} & 64 \\
    WebKit & \cite{webkit} & 1031 \\
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & 36,452 \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued by our team since April,
    2018. The analysis of warnings was not uninterrupted.}
  \label{tab:bugs}
  \begin{tabular}{cccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Priority & Seed \\
    \midrule    
    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & HI & webkit.jstests.es6 \\ 
    2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979} & HI & webkit.jstests.es6 \\
    3  & 4/14 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}  & HI & webkit.jstests.es6    \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749} & HI & JerryScriptjs.ecma      \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033} & HI & mozilla      \\
    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038} & HI & JerryScriptjs.ecma   \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065} & HI & mozilla
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} & \multirow{2}{*}{HI} & \multirow{2}{*}{mozilla}\\
                        &  &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}  &   & \\
    \midrule    
    9  & 4/29 & radamsa & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}  & HI  & JerryScriptjs.ecma\\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} & \multirow{2}{*}{HI} & \multirow{2}{*}{tinyjs.tests}\\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156} &  & 
    \\
    \midrule    
    11 & 5/02 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197} & LO & mozilla \\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208} & HI & mozilla \\
    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} & HI & JerryScriptjs.regression \\
    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} & HI & v8.test.benchmarks\\
    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} & HI & webkit.jstests.es6\\
    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} & LO & mozilla\\
    17 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943} & HI & webkit.jstests.es6\\
    18 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScriptjs.regression\\
    19 & 6/28 & \crossmark & Chakra & Confirmed  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & webkit.jstests.es6\\
    20 & 7/10 & quickfuzz & JavaScriptCore & New  & \href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520} & HI & x\\
    21 & 7/10 & quickfuzz & Chakra & New  & \href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443} & HI & x\\    
    \midrule
    \multirow{2}{*}{22}  & \multirow{2}{*}{7/10} &  \multirow{2}{*}{quickfuzz} & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442} & \multirow{2}{*}{HI} & \multirow{2}{*}{x}\\
                        &  &                       &
    JavascriptCore & New & \href{https://bugs.webkit.org/show_bug.cgi?id=187519}{\#187519}  &   & \\
   \bottomrule     
  \end{tabular}
\end{table*}

@@

\subsection{False Positives Bugs}

An example of a warning from the HI group is defined in Figure~\ref{fig:hi-priority}. 
This is a testcase from WebKit.es6 suite that it was mutate by radamsa fuzzer, the 
initial seed has in line 3 the code \CodeIn{"foo".repeat(3)} but the fuzzer changed the 
integer 3 to a big integer number. We reported this case in chakra due a core dumps that occurs
during the runtime, however this case was rejected due \CodeIn{incompatibility by design} that
this is an intentional behavior of engine that crash the process if it runs out of memory
\cite{bug4979}.

% \subsection{LO bugs}
% 
% \Igor{For example, a bug caught by our environment and reported as LO priority was reported 
% on Chakra engine, the JS code can be found in Figure~\ref{fig:lo-priority}. In this case,
% this is a seed from Mozilla suite (\CodeIn{mozilla/non262/statements/for-in-with-assignments.js}),
% the warning was not caught by the \CodeIn{assertEq} function that compares if two arguments are equals, 
% the bug appears inside the generator function\footnote{Generators \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Statements/function*}}
% at line 2. According to ES6 specification\footnote{ES6 YieldExpression \url{https://www.ecma-international.org/ecma-262/8.0/index.html\#prod-YieldExpression}},
% it is allowed the use of \CodeIn{yield in} in a \CodeIn{for} loop. In our infrastructure,
% only Chakra engine fails with an error output \CodeIn{SyntaxError: Syntax error}, due
% the output does not shows nothing related with assertions, we considered this one as a warning from LO group.
% Until now, the issue was confirmed and waiting for merge/closed.
% \Fix{checar ate o prazo de submissao. Essa issue esta confirmada e com commits, falta apenas o merge.}
% }
% \begin{figure}[h!]
%   \centering
%   \scriptsize
%   \lstset{escapeinside={@}{@},
%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
%     basicstyle=\ttfamily\scriptsize, boxpos=c,
%     numberstyle=\tiny,
%     morekeywords={assertEq, var, yield, in, function},
%   }
%   \begin{lstlisting}
% function* g1() {
%   for (var x = yield in {}) ;
% }
% var it = g1();
% assertEq(it.next().done, false);
% assertEq(it.next().done, true);
%   \end{lstlisting}
%   \normalsize
%   \caption{Bug caught by our environment as LO priority.}
%   \label{fig:lo-priority}
%   \end{figure}
